A Systematic Literature Review on Extensions to Role-Based Access Control

### 2014-02-09 paper/sections/categorization.tex
updates: RQ formats and combine of RQ3-4 fixing typos and some sentences.

\section{Categorization} \label{sec:categorization}

RQ1: What categories exist within the RBAC extension models?

During the paper reading phase, we identify categorical themes, which are
central topic or context of the RBAC extension models. 
For example, the paper ``Privacy-aware role-based access control'' \cite{ni2010privacy} brings in the notion of privacy explicitly within the title of the paper and the name of their model. 
Some papers presented this direct pronouncement of theme of the RBAC extension models, whereas others were less obvious. 
Thus, we developed a set of guidelines to aide in determining a set of eight categories based upon observations during the paper reading phase. 
In developing these guidelines, we defined each category by a single noun-phrase descriptor.
The guidelines were as follows:

@@

  \item \textbf{Spatial}: The RBAC extension model provides spatial constraints, location-based constraints in specifying access
	control policies. For example, in organizations, locations are enforced whereas a
	specific role is permitted to conduct an action. Consider that a part-time employee works only in a specific location.
	In such cases, the part-time employee role should access required resources only when the user is in that location. 
	Spatial constraints can integrate with roles, user-role assignments, or role-permission assignments.

  \item \textbf{Temporal (Temp)}:  The RBAC extension model provides temporal constraints, time-based constraints in specifying access
	control policies. For example, in organizations, periodic temporal durations are enforced whereas a
	specific role is permitted to conduct an action. Consider that a part-time employee works only from 9:00 a.m. to 3:00 p.m.
	In such cases, the part-time employee role should be allowed to access required resources during the interval. 
	Temporal constraints can integrate with roles, user-role assignments, or role-permission assignments.

>>>>

\section{RQ1: Classification} \label{sec:categorization}

\textit{How can RBAC extension models be classified?}

During the paper reading phase, we identify classification themes, which are
central topic or context of the RBAC extension models. Our classification process
yields a set of categories based upon observations during the paper reading phase.
For example, the paper ``Privacy-aware role-based access control'' \cite{ni2010privacy} brings in the notion of privacy explicitly within the title of the paper and the name of their model. We classify this paper into the Privacy category. Some papers presented this direct pronouncement of theme of the RBAC extension models, whereas others were less obvious.
Thus, we developed a set of guidelines to aide in determining a set of eight categories. 
In developing these guidelines, we defined each category by a single noun-phrase descriptor.
The guidelines were as follows:

@@

  \item \textbf{Spatial}: The RBAC extension model provides spatial constraints, location-based constraints in specifying access
	control policies. For example, in organizations, locations are enforced whereas a
	specific role is permitted to conduct an action. Consider that a temporal employee works only in a specific location.
	In such cases, the temporal employee role should access required resources only when the user is in that location. 
	Spatial constraints can integrate with roles, user-role assignments, or role-permission assignments.

  \item \textbf{Temporal (Temp)}:  The RBAC extension model provides temporal constraints, time-based constraints in specifying access
	control policies. For example, in organizations, periodic temporal durations are enforced whereas a
	specific role is permitted to conduct an action. Consider that a temporal employee works only from 9:00 a.m. to 3:00 p.m.
	In such cases, the temporal employee role should be allowed to access required resources during the interval. 
	Temporal constraints can integrate with roles, user-role assignments, or role-permission assignments.
